The increasing cost of happiness

### 2020-09-05 src/The increasing cost of happiness.Rmd
Updated to github_document

---
title: "The increasing cost of happiness"
author: "Dr Richard Morris"
date: "Updated: `r Sys.Date()`"
bibliography: references.bib
csl: elsevier-harvard.csl
output: 
  html_document:
    keep_md: true
---

>>>>

---
title: "The increasing cost of happiness"
author: "Dr Richard Morris"
date: "Updated: `r Sys.Date()`"
bibliography: references.bib
csl: elsevier-harvard.csl
output: github_document
---
